Computer Science House By-Laws

### 2016-11-10 bylaws.tex
Eboard decides budget

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\bsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant an extension for payment.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\\*\\*
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
\bsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{l c}
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

The suggested total operational budget is \$8064.
This figure is based on yearly estimated on-floor member dues (\$160 x 56 members = \$8960) minus the 10\% reserved for Accumulated (Accum).
Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 60\% majority vote at a House Meeting.
 	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
 	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
 	This may occur only once per Introductory Evaluation Process.\bsection{Code of Conduct}
\end{enumerate}

>>>>

% BY-LAW III - OPERATIONS OF THE FINANCIAL DIRECTORSHIP
\bylaw{Operations of the Financial Directorship}
\bsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\bsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\\*\\*
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant an extension for payment.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may grant an extension.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
This process may be repeated indefinitely at the discretion of the Financial Director and the Executive Board.
\\*\\*
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}). After this date, dues collection is suspended until the start of the next academic year.
\bsection{Derivation of Directorship Budgets}
At the start of each operating session the Executive Board will create a proposed budget. Said budget will define the percentage of funds allotted for each director and what portion will be set aside for deposit into Computer Science House's accumulated funds. The total operational budget is to be defined by the Financial Director based on dues collection.
\\*\\*
In order for the budget to take effect it must pass a Two-Thirds Majority Executive Board vote with the Financial Director in favor.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
